### 2019-04-03 papers/journal/abstract.tex
Updated abstarct

Vesicle Traffic Systems (VTSs) transport cargo among the intracellular compartments of eukaryotic biological cells.
%
The compartments are viewed as nodes that are labeled by their chemical identity and the transport vesicles are similarly viewed as labeled edges between the nodes.
%
Several interesting questions about VTSs translate to combinatorial search and synthesis problems. 
%
We present novel SAT, SMT and QBF based encodings of the properties over vesicle traffic systems and a tool that searches for the networks that satisfy properties that are related to transport consistency conditions using these solvers. 
%
In our numerical experiments, we show that our tool can search for networks of sizes that are relevant to real cellular systems.

% Vesicle Traffic Systems(VTSs) are the material transport 
% mechanisms among the compartments inside the biological cells.

>>>>

Vesicle Traffic Systems (VTSs) transport cargo among the intracellular compartments of eukaryotic biological cells.
%
The compartments are viewed as nodes that are labeled by their chemical identity and the transport vesicles are similarly viewed as labeled edges between the nodes.
%
Several interesting questions about VTSs translate to combinatorial search and synthesis problems. 
%
We present novel encoding based on Boolean satisfiability (SAT), satisfiability modulo theories (SMT) and quantified Boolean formula (QBF) of the properties over vesicle traffic systems.
%
We have implemented the presented encoding in a tool that searches for the networks that satisfy properties related to transport consistency conditions using these solvers. 
%
In our numerical experiments, we show that our tool can search for networks of sizes that are relevant to real cellular systems.
%
%Understanding VTSs is an ongoing area of research and for many cells they are partially known. 
%
%We do not have a complete picture of the VTS graph, and in many cases we know only partial information known.
%
The biological VTS graphs known to date are incomplete in the sense that we do not know all the edges, and we also do not know all the molecules that populate the edges and the nodes of the VTS.
%Complete picture of VTSs are not clear and only partial 
%For example, there may be undiscovered edges, nodes, or their labels in a VTS of a cell. 
%
%In this sense the picture of the VTS graphs is only partially complete. 
%
It has been speculated that there are properties that the VTSs must satisfy.
For example, stability, i.e., every chemical that is leaving a compartment
comes back. 
%
\todo{Text below this is just a copy of last paper}Many synthesis questions may arise in this scenario, where we want to complete a partially known VTS under a given property.
%
In the paper, we present novel encodings of the above questions into
the QBF satisfiability problems. 
%
We have implemented the encodings in a highly configurable tool and applied to a couple of VTSs found in the literature and to several synthetic graphs.
%
Our results demonstrate that our method can scale up to the graphs of interest.
% Vesicle Traffic Systems(VTSs) are the material transport 
% mechanisms among the compartments inside the biological cells.

### 2019-04-03 papers/journal/property.tex
Uniform use of the title without :
Updated abstarct

We analyze the model against our desired properties.
%
\ankit{Not completely correct}Since in biology there are no declared specifications or properties,
we conjecture some properties that appear to be true in all the known
biological systems.
%
In this paper, we choose graph connectedness to be a key property.
%
We will also seek two kinds of questions give the property.
% %
% In this paper,
% our conjecture relates graph-connectedness to a particular variation of SNARE pairing and
% regulation rules of the VTS.
% %
% We are interested in the following two type of properties of the transport graph:
\begin{enumerate}
\item {\em Existential condition:}
if there is a VTS that satisfies the connectedness property.

@@

\subsubsection{Search for universal condition}
%
% Similarly, for the conjecture that k-connectedness is a universal condition for the VTS,
For some $k>0$,
we have to ensure that every graph of $k$-connected structure satisfies all
the rules of the system.
%
We also aim to find the minimum $k$. 
% We also have to ensure that the particular k is the least one. 
%
This condition can be specified as: for every k-connected graph, there exists a satisfiable assignment following the rules of the system. 
%
% \begin{align*}
%   & \forall G \, \texttt{Connectivity(k)} \implies  \exists
%                         f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
%   \tag{U}\label{eq:univcond}
% \end{align*}
%
We will use the same procedure as the existential condition to ensure the k to be the least one.
%
The formula for the problem has quantifier alternation. 
%
Most SAT solvers can check (at least efficiently) only quantifier-free formulas.
%
We need a QBF solver for such queries.
%
%To handle this challenge, we used a combination of nondeterminism and Boolean enumeration at the C-source level to eliminate quantifiers, as explained further below.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

\noindent We analyze the model against our desired properties.
%
Since in biology there are no declared specifications or properties,
we conjecture some properties that appear to be 
%true in 
relevant in
all the known
biological systems.
%
In this paper, we choose graph connectedness to be a key property.
%
We will also seek two kinds of questions give the property.
% %
% In this paper,
% our conjecture relates graph-connectedness to a particular variation of SNARE pairing and
% regulation rules of the VTS.
% %
% We are interested in the following two type of properties of the transport graph:
\begin{enumerate}
\item {\em Existential condition:}
if there is a VTS that satisfies the connectedness property.

@@

\subsubsection{Search for universal condition}
%
% Similarly, for the conjecture that k-connectedness is a universal condition for the VTS,
For some $k>0$,
we have to ensure that every graph of $k$-connected structure satisfies all
the rules of the system.
%
We also aim to find the minimum $k$. 
% We also have to ensure that the particular k is the least one. 
%
This condition can be specified as: for every k-connected graph, there exists a satisfiable assignment following the rules of the system. 
%
% \begin{align*}
%   & \forall G \, \texttt{Connectivity(k)} \implies  \exists
%                         f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
%   \tag{U}\label{eq:univcond}
% \end{align*}
%
We will use the same procedure as the existential condition to ensure the k to be the least one.
%
The formula for the problem has quantifier alternation. 
%
Most SAT solvers can check (at least efficiently) only quantifier-free formulas.
%
We need a QBF solver for such queries.
%
%To handle this challenge, we used a combination of nondeterminism and Boolean enumeration at the C-source level to eliminate quantifiers, as explained further below.
%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
